\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}

\begin{document}

\title{Radix-2 FFT in C++20: Correctness-Centered Design, Mathematical Rigor, and Automated Verification}

\author{
\IEEEauthorblockN{1\textsuperscript{st} Santiago Florido Gómez}
\IEEEauthorblockA{\textit{Mechatronic engineer} \\
\textit{ENSTA - Paris}\\
Paris, France \\
santiago.florido@ensta-paris.fr}
}

\maketitle

\begin{abstract}
\input{dsections/abstract}
\end{abstract}

\begin{IEEEkeywords}
fast Fourier transform, mixed-radix, split-radix, radix-2, Cooley-Tukey, spectral analysis, numerical verification, C++20
\end{IEEEkeywords}

\input{dsections/introduction}
\input{dsections/mathematical_foundations}
\input{dsections/algorithm_and_implementation}
\input{dsections/mixed_radix_42_fft}
\input{dsections/split_radix_fft}
\input{dsections/verification}
\input{dsections/results_comparison}
\input{dsections/applications}
\input{dsections/conclusion}

\section*{Acknowledgment}
This work did not receive external funding.

\begin{thebibliography}{00}
\bibitem{cooley1965}
J. W. Cooley and J. W. Tukey, "An algorithm for the machine calculation of complex Fourier series," \textit{Mathematics of Computation}, vol. 19, no. 90, pp. 297--301, 1965.

\bibitem{oppenheim1999}
A. V. Oppenheim, R. W. Schafer, and J. R. Buck, \textit{Discrete-Time Signal Processing}, 2nd ed. Upper Saddle River, NJ, USA: Prentice Hall, 1999.

\bibitem{bracewell2000}
R. N. Bracewell, \textit{The Fourier Transform and Its Applications}, 3rd ed. New York, NY, USA: McGraw-Hill, 2000.

\bibitem{frigo2005}
M. Frigo and S. G. Johnson, "The design and implementation of FFTW3," \textit{Proceedings of the IEEE}, vol. 93, no. 2, pp. 216--231, Feb. 2005.

\bibitem{ieee754}
IEEE Standard for Floating-Point Arithmetic, IEEE Std 754-2019, 2019.
\end{thebibliography}

\end{document}
